Eddy covariance towers as sentinels of abnormal radioactive material releases

### 2025-02-24 manuscript/manuscript.tex
add paper doi

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.000/XXXXX}}
\renewcommand{\undertitle}{This is a draft of a Manuscript intended for Environmental Science and Pollution Research \\ \href{https://doi.org/10.1000/XXXXX}{DOI: 10.1000/XXXXX}}
\renewcommand{\shorttitle}{Eddy covariance towers as sentinels}

>>>>

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/10.1007/s11356-025-36171-3}{DOI: 10.1007/s11356-025-36171-3}}
\renewcommand{\undertitle}{This is an Accepted Manuscript of an article in Environmental Science and Pollution Research \\ \href{https://doi.org/10.1000/10.1007/s11356-025-36171-3}{DOI: 10.1000/10.1007/s11356-025-36171-3}}
\renewcommand{\shorttitle}{Eddy covariance towers as sentinels}
